---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# samplr

<!-- badges: start -->
<!-- badges: end -->

The goal of samplr is to illustrate the workflow to create a minimal package.

## Installation

You can install the development version of samplr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("paezha/samplr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(samplr)
## basic example code
```

Package {samplr} includes a single data object, which can be loaded like so:
```{r data}
data("energy_and_emissions")
```

Here is a scatterplot of population by country and $CO_2$ emissions in 2015:
```{r scatterplot, echo = FALSE}
plot(energy_and_emissions$Population, 
     energy_and_emissions$CO2_2015,
     main = "Scatterplot",
     xlab = "Country population", ylab = "CO2 emissions (kilotonnes, 2015)",
     pch = 19, 
     frame = FALSE)
```
